GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University

### 2024-10-31 ennv.tex
updates

First, \dd{} initializes the activation pattern set \functiontextformat{ActPatterns} with an empty activation pattern $\emptyset$. Then \dd{} enters a loop (\autoref{line:dpllstart}-\autoref{line:dpllend}) to search for a satisfying assignment or a proof of unsatisfiability. In the first iteration, \dd{} selects the only available activation pattern $\emptyset \in \functiontextformat{ActPatterns}$. 
It calls \functiontextformat{Deduce} to check the feasibility of the problem based on the current activation pattern. \functiontextformat{Deduce} uses abstraction to approximate that from the input constraints the output values are feasible for the given network. 
Since \functiontextformat{Deduce} cannot decide infeasibility, \dd{} randomly selects a neuron to split (\functiontextformat{Decide}). Let us assume that it chooses $v_4$ to split, which essentially means the problem is split into two independent subproblems: one with $v_4$ active and the other with $v_4$ inactive.
\dd{} then adds $v_4$ and $\overline{v_4}$ to \functiontextformat{ActPatterns}.

@@

\section{Interval}
\section{Zotope}
\section{Polytope}

>>>>

First, \dd{} initializes the activation pattern set \functiontextformat{ActPatterns} with an empty activation pattern $\emptyset$. Then \dd{} enters a loop (\autoref{line:dpllstart}-\autoref{line:dpllend}) to search for a satisfying assignment or a proof of unsatisfiability. In the first iteration, \dd{} selects the only available activation pattern $\emptyset \in \functiontextformat{ActPatterns}$. 
It calls \functiontextformat{Deduce} to check the feasibility of the problem based on the current activation pattern. \functiontextformat{Deduce} uses abstraction to approximate that from the input constraints the output values are feasible for the given network. 
Since \functiontextformat{Deduce} cannot decide infeasibility, \dd{} randomly selects a neuron to split (\functiontextformat{Decide}). Let us assume that it chooses $v_4$ to split, which essentially means the problem is split into two independent subproblems: one with $v_4$ active and the other with $v_4$ inactive.
\dd{} then adds $\{v_4\}$ and $\{\overline{v_4}\}$ to \functiontextformat{ActPatterns}.

@@

\section{Interval}

An interval abstraction is a simple and widely-used abstraction technique in DNN verification. It approximates the range of values that a neuron can take by using a lower and upper bound $[l, u]$. The interval abstraction is efficient and easy to implement, but it can be imprecise, especially for non-linear activation functions like ReLU.

\paragraph{Example}: For the DNN in \autoref{fig:dnn}, the interval abstraction for the input layer is $x_1 \in [-1, 1]$ and $x_2 \in [-2, 2]$. The interval abstraction for the hidden layer is $x_3 \in [0, 2]$ because $x_3 = [ReLU(-0.5x_1 + 0.5x_2 + 1.0), ReLU(-0.5x_1 + 0.5x_2 + 1.0)] = [ReLU(-0.5 \times -1 + 0.5 \times -2 + 1.0), ReLU(-0.5 \times 1 + 0.5 \times 2 + 1.0)] = [0, 2]$. Similarly, $x_4 \in [0, 2]$. The interval abstraction for the output layer is $x_5 \in [-3, 3]$.

\section{Zotope}
\section{Polytope}
